Search-Based Test Data Generation for JavaScript Functions with DOM

### 2018-01-23 doc/icse2018/icse2018.tex
Continue working on the paper. Test for measuring the significance.

\begin{figure}[t!]
  \centering 
  \begin{sequencediagram}[font=\footnotesize]

    \renewcommand\unitfactor{0.5}
    \newinst{user}{\textbf{User}}
    \newinst{server}{\textbf{Server}}
    \newinst[1]{validator}{\textbf{Validator}}
    \newinst{client}{\textbf{Client}}

@@

      \begin{sdblock}{\textbf{Genetic Loop}}{\hspace{2mm}$\text{branch} \in \text{branches}'$}
        \begin{sdblock}{\textbf{Random Loop}}{errors > 0}
          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
          \end{call}
          \prelevel
        \end{sdblock}

        \begin{sdblock}{\textbf{Fitness Loop}}{(fitness $\neq$ 0) $\vee$ gen.limit}

          \begin{sdblock}{\textbf{Evaluation Loop}}{p $\in$ pop}
            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
            \end{call}

@@

          \begin{sdblock}{\textbf{Crossover Loop}}{errors > 0}
            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
            \end{call}
            \prelevel
          \end{sdblock}

          \begin{sdblock}{\textbf{Mutation Loop}}{errors > 0}
            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
            \end{call}
            \prelevel
          \end{sdblock}

@@

Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $B_f$. We implemented such a framework as a client-server application which under the hood uses the genetic engine for test generation. The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}. The diagram consists of the four interacting components \User, \Server, \Validator, and \Client. \Server is the key component of the whole framework. It is responsible for the \emph{Initialization Phase} and the \emph{Genetic Phase}. Both phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.

@@

During the \emph{Initialization Phase} we analyze the FUN in order to retrieve the data required for the consecutive genetic testing. The main steps of this phase are illustrated by Algorithm~\ref{alg.init}. Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}. In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect constant info. Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods:
\begin{multicols}{2}
\footnotesize
\begin{itemize}
\item \texttt{getElementsByTagName}
\item \texttt{getElementById}
\item \texttt{getElementsByClassName}
\item \texttt{getElementsByName}
\end{itemize}
\end{multicols}
which respectively signify the reference to the \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} encountered in the FUT. Next step is normalizing the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g. transform \emph{if-then} branches into \emph{if-then-else}. We instrument the FUT (line~\ref{alg.init.instr}) in order to collect the run-time data such as the execution trace, the approach level, the branch and loop distances, and the constants. Upon the $ifun$ execution this information is gathered and fed back to the fitness evaluation procedure. Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).

@@

@@

\begin{table*}[t]
  \caption{Summary of the Case-Studies}
  \label{tbl.case.studies}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{l|c|l|l|r|r|r|r|r|r|c|c|c|c}
    \textbf{case-study} & \textbf{?} & \textbf{function} & \textbf{type signature} & \textbf{\#LOC} & \textbf{\#BR} & \textbf{\#D} & \textbf{CC} & \textbf{HV} & \textbf{MI} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
    sudoku     & + & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & 344 & 107.58 & + & + & + & - \\
    sudoku     & + & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & 370 & 112.55 & + & + & + & + \\
    sudoku     & + & newGame & (dom)           & 9  & 1 & 2 & 2 & 326 & 115.15 & + & + & + & + \\
    sudoku     & + & revealAll & (dom)         & 8  & 0 & 2 & 1 & 312 & 117.44 & + & + & + & - \\
    sudoku     & - & showCell & (dom)         & 8  & 0 & 0 & 1 & 232 & 118.46 & + & + & + & - \\
    sudoku     & + & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & 555 & 97.9   & + & - & + & - \\
    sudoku     & - & switchLevel & (dom,bool) & 10 & 1 & 2 & 2 & 257 & 114.26 & + & - & + & - \\
    phormer    & + & toggleInfo & (dom,string)                                                      & 16 & 3 & 1 & 4 & 570  & 103.46 & + & + & - & - \\
    phormer    & - & update & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) & 35 & 5 & 3 & 6 & 1190 & 87.804 & + & + & - & - \\
    phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & 361  & 105    & + & + & - & - \\
    hotel RS   & - & RequiredField & (dom,[string]) & 11 & 2 & 2 & 5 & 247  & 112.16 & + & + & - & - \\
    hotel RS   & + & isValidCard & ([int])           & 17 & 2 & 2 & 5 & 351  & 103.91 & - & - & - & - \\
    hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & 130  & 126.67 & - & - & - & - \\
    hotel RS   & + & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & 104  & 124.71 & - & - & - & - \\
    hotel RS   & - & validateNumber & (dom,string)  & 7  & 1 & 1 & 4 & 98.1 & 122.87 & + & + & - & - \\
    apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & 242 & 114.1  & + & + & - & -\\
    apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & 212 & 123.19 & + & + & - & - \\
    apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & 539 & 104.70 & - & - & - & - \\
    apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & 410 & 104.82 & + & + & - & - \\
    apophis    & + & initShields & (dom,[int],int,int)                                               & 6  & 0 & 1 & 1 & 310 & 122.12 & + & + & - & -\\
    bingbong   & + & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & 305  & 119.45 & + & + & - & - \\
    bingbong   & + & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & 353  & 106.38 & + & + & - & - \\
    bingbong   & + & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & 2380 & 72.594 & + & + & - & - \\
    bingbong   & - & drawLevel & (dom,int,int,int,int)                       & 22 & 2  & 3 & 3  & 703  & 97.816 & + & + & - & - \\
    bingbong   & - & goPing & (dom,int,int,int)                              & 12 & 2  & 2 & 3  & 268  & 110.93 & + & + & - & - \\
    burncanvas & + & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & 583 & 86.214 & - & - & - & - \\
    cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & 308 & 101.49 & -  & -  & - & - \\
    cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & 309 & 101.38 & -  & -  & - & - \\ 
    mathjs     & + & prob\_gamma & (float)                                    & 57 & 8  & 2 & 16 & 1370 & 77.121 & - & - & - & - \\
%}
\end{table*}

\subsection{Research Questions}
\label{sub.sec.research.questions}

\begin{description}
\item[\textbf{RQ1:}] What is the performance of our test generation framework? Is there any difference in performance on examples with DOM and without?  Which algorithm works best random, genetic or genetic with restart?
\item[\textbf{RQ2:}] What is the cost of one iteration of each algorithm?
\item[\textbf{RQ3:}] How does the branch coverage progress over time given a fixed budget per branch? 
\end{description}

@@

      \multirow{2}{*}{\textbf{NAME}} & \multirow{2}{*}{\textbf{\#D}}         &  \multicolumn{3}{c|}{$m_r$} & \multicolumn{3}{c|}{$m_g$} & \multicolumn{3}{c|}{$m_{g10}$} & \multirow{2}{*}{$\frac{t_r}{t_g}$} &  \multirow{2}{*}{$\frac{t_r}{t_{g10}}$} & \multirow{2}{*}{$\frac{t_g}{t_{g10}}$}   & \multirow{2}{*}{$a_{rg}$} &  \multirow{2}{*}{$a_{rg10}$} & \multirow{2}{*}{$a_{gg10}$} \\

@@

    $(3,4,\inFor)$    & 1        & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & 0.57 & 0.39 & 0.37  \\
    $(5,6,\thenBr)$   & 2        & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & 0.46 & 0.5  & 0.53  \\
    $(5,15,\elseBr)$  & 2        & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & 0.48  \\
    $(9,10,\thenBr)$  & 3        & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & 0.40  \\
    $(9,14,\elseBr)$  & 3        & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & 0.56 & 0.51 & 0.45  \\

@@

    $(7,8,\thenBr)$   & 2        & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & 0.6  & 0.66 & 0.43   \\
    $(10,11,\thenBr)$ & 3        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & 0.48   \\
    $(10,14,\elseBr)$ & 3        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & 0.55 & 0.55 & 0.46   \\

@@

    $(6,7,\thenBr)$   & 2        & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & 0.5  \\

@@

    $(2,3,\inFor)$    & 1        & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & 0.45 & 0.39 &  0.43  \\
    $(4,5,\inFor)$    & 2        & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & 0.55 &  0.37  \\

@@

    $(13,14,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & 0.58 & 0.53 & 0.46  \\
    $(17,18,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & 0.46 & 0.47 & 0.5   \\

@@

    $(2,3,\thenBr)$   & 1        & 2        & 2    & 1         & 2  & 2 & 1                 & 2 & 1   & 0.5                & 1     & 2     & 2     & 0.54 & 0.58 & 0.55  \\
    $(6,7,\thenBr)$   & 1        & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & 0.48  \\

@@

    $(3,6,\elseBr)$   & 1        & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & 0.5   \\
    $(7,8,\inFor)$    & 1        & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & 0.43  \\
    $(10,11,\thenBr)$ & 2        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & 0.43  \\
    $(10,13,\elseBr)$ & 2        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & 0.38  \\
    $(14,15,\inFor)$  & 1        & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & 0.55  \\

@@

    $(2,3,\thenBr)$   & 1        & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & 0.59  \\

@@

    $(2,3,\inFor)$    & 1        & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & 0.53  \\

@@

    $(2,3,\thenBr)$   & 1        & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & 0.56  \\

@@

    $(10,11,\thenBr)$ & 1        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & 0.43 & 0.94 \\

@@

    $(6,7,\thenBr)$   & 1        & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & 0.53 & 0.5  & 0.5   \\
    $(6,10,\elseBr)$  & 1        & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & 0.4   \\
    $(11,12,\thenBr)$ & 2        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & 0.41  \\
    $(11,15,\elseBr)$ & 2        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & 0.47  \\
    $(16,17,\thenBr)$ & 3        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & 0.45  \\
    $(16,20,\elseBr)$ & 3        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & 0.46  \\

@@

    $(21,25,\elseBr)$ & 4        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & 0.42  \\
    $(29,30,\thenBr)$ & 1        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & 0.5   \\
    $(29,37,\elseBr)$ & 1        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.63 & 0.53 & 0.43  \\
    $(38,39,\thenBr)$ & 2        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & 0.54  \\
    $(38,46,\elseBr)$ & 2        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & 0.58 & 0.44  \\
    $(47,48,\thenBr)$ & 3        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & 0.54  \\
    $(47,55,\elseBr)$ & 3        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & 0.46  \\

>>>>

\begin{figure}[t!]
  \centering 
  \begin{sequencediagram}[font=\scriptsize]

    \renewcommand\unitfactor{0.35}
    \newinst{user}{\textbf{User}}
    \newinst{server}{\textbf{Server}}
    \newinst[1]{validator}{\textbf{Validator}}
    \newinst{client}{\textbf{Client}}

@@

      \begin{sdblock}{\textbf{Genetic Loop}}{\scriptsize \hspace{8mm}$\text{branch} \in \text{branches}'$}
        \begin{sdblock}{\textbf{Random Loop}}{\scriptsize errors > 0}
          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
          \end{call}
          \prelevel
        \end{sdblock}

        \begin{sdblock}{\textbf{Fitness Loop}}{\scriptsize (fitness $\neq$ 0) $\vee$ gen.limit}

          \begin{sdblock}{\textbf{Evaluation Loop}}{\scriptsize p $\in$ pop}
            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
            \end{call}

@@

          \begin{sdblock}{\textbf{Crossover Loop}}{\scriptsize errors > 0}
            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
            \end{call}
            \prelevel
          \end{sdblock}

          \begin{sdblock}{\textbf{Mutation Loop}}{\scriptsize errors > 0}
            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
            \end{call}
            \prelevel
          \end{sdblock}

@@

Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $B_f$. Our JS testing framework, called \emph{JEDI}, is a client-server application which under the hood uses the genetic engine for test generation. The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}. The diagram consists of the four interacting components \User, \Server, \Validator, and \Client. \Server is the key component of the whole framework. It is responsible for the \emph{Initialization Phase} and the \emph{Genetic Phase}. Both phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.

@@

During the \emph{Initialization Phase} we analyze the FUN in order to retrieve the data required for the consecutive genetic testing. The main steps of this phase are illustrated by Algorithm~\ref{alg.init}. Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}. In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect constant info. Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, and \texttt{getElementsByName},
which respectively signify the reference to the \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} encountered in the FUT. Next step is normalizing the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g. transform \emph{if-then} branches into \emph{if-then-else}. We instrument the FUT (line~\ref{alg.init.instr}) in order to collect the run-time data such as the execution trace, the approach level, the branch and loop distances, and the constants. Upon the $ifun$ execution this information is gathered and fed back to the fitness evaluation procedure. Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).

@@

By carrying the evaluation, we would like to address the following research questions:
\begin{description}
\item[\textbf{RQ1 (performance):}] What is the performance of our test generation framework? Is there any difference in performance on examples with DOM and without?  Which algorithm works best random, genetic or genetic with restart?
\item[\textbf{RQ2 (cost):}] What is the cost of one iteration of each algorithm?
\item[\textbf{RQ3 (coverage):}] How does the branch coverage progress over time given a fixed budget per branch?
\item[\textbf{RQ4 (significance):}] What is statistical significance and effect size of our experimental results? 
\end{description}

@@

\setlength\tabcolsep{0.6pt}
\begin{table}[t]
  \caption{Summary of the Case-Studies}
  \label{tbl.case.studies}
  %\resizebox{\textwidth}{!}{
    \scriptsize
  \begin{tabular}{l|l|p{3.1cm}|c|c|c|c|c|c|c|c}
    \toprule
    \textbf{case-study} & \textbf{function} & \textbf{type signature} & \textbf{LOC} & \textbf{BR} & \textbf{D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
    \hline
    sudoku     & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
    sudoku     & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & + & + & + & + \\
    sudoku     & newGame & (dom)           & 9  & 1 & 2 & 2 & + & + & + & + \\
    sudoku     & revealAll & (dom)         & 8  & 0 & 2 & 1 & + & + & + & - \\
    %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
    sudoku     & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & + & - & + & - \\
    %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
    \hline
    phormer    & toggleInfo & (dom,string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
    %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
    %%            &   &        &                                                                      & 35 & 5 & 3 & 6 & + & + & - & - \\
    %% phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & + & + & - & - \\
    \hline
    %% hotel RS   & - & RequiredField & (dom,[string])  & 11 & 2 & 2 & 5 & + & + & - & - \\
    hotel RS   & isValidCard & ([int])           & 17 & 2 & 2 & 5 & - & - & - & - \\
    %% hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & - & - & - & - \\
    hotel RS   & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & - & - & - & - \\
    %% hotel RS   & - & validateNumber & (dom,string)   & 7  & 1 & 1 & 4 & + & + & - & - \\
    \hline
    %% apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & + & + & - & -\\
    %% apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & + & + & - & - \\
    %% apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & - & - & - & - \\
    %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
    apophis    & initShields & (dom,[int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
    \hline
    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
    bingbong   & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
    bingbong   & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
    %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
    %% bingbong   & - & goPing & (dom,int,int,int)                               & 12 & 2  & 2 & 3  & + & + & - & - \\
    \hline
    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & - & - & - & - \\
    %% \hline
    %% cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & -  & -  & - & - \\
    %% cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & -  & -  & - & - \\ 
    \hline
    mathjs     & prob\_gamma & (float)                                   & 57 & 8  & 2 & 16 & - & - & - & - \\
    \bottomrule
  \end{tabular}
%}
\end{table}

@@

      \multirow{2}{*}{\textbf{NAME}} & \multirow{2}{*}{\textbf{\#D}}         &  \multicolumn{3}{c|}{$m_r$} & \multicolumn{3}{c|}{$m_g$} & \multicolumn{3}{c|}{$m_{g10}$} & \multirow{2}{*}{$\frac{t_r}{t_g}$} &  \multirow{2}{*}{$\frac{t_r}{t_{g10}}$} & \multirow{2}{*}{$\frac{t_g}{t_{g10}}$}   & \multirow{2}{*}{r/g} &  \multirow{2}{*}{r/g10} & \multirow{2}{*}{g/g10} \\

@@

    $(3,4,\inFor)$    & 1        & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
    $(5,6,\thenBr)$   & 2        & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
    $(5,15,\elseBr)$  & 2        & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
    $(9,10,\thenBr)$  & 3        & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
    $(9,14,\elseBr)$  & 3        & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\

@@

    $(7,8,\thenBr)$   & 2        & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
    $(10,11,\thenBr)$ & 3        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
    $(10,14,\elseBr)$ & 3        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\

@@

    $(6,7,\thenBr)$   & 2        & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\

@@

    $(2,3,\inFor)$    & 1        & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
    $(4,5,\inFor)$    & 2        & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\

@@

    $(13,14,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
    $(17,18,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\

@@

    $(2,3,\thenBr)$   & 1        & 2        & 2    & 1         & 2  & 2 & 1                 & 2 & 1   & 0.5                & 1     & 2     & 2     & - & - & -  \\
    $(6,7,\thenBr)$   & 1        & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\

@@

    $(3,6,\elseBr)$   & 1        & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
    $(7,8,\inFor)$    & 1        & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
    $(10,11,\thenBr)$ & 2        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
    $(10,13,\elseBr)$ & 2        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
    $(14,15,\inFor)$  & 1        & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\

@@

    $(2,3,\thenBr)$   & 1        & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\

@@

    $(2,3,\inFor)$    & 1        & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\

@@

    $(2,3,\thenBr)$   & 1        & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\

@@

    $(10,11,\thenBr)$ & 1        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\

@@

    $(6,7,\thenBr)$   & 1        & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
    $(6,10,\elseBr)$  & 1        & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
    $(11,12,\thenBr)$ & 2        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
    $(11,15,\elseBr)$ & 2        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
    $(16,17,\thenBr)$ & 3        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
    $(16,20,\elseBr)$ & 3        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\

@@

    $(21,25,\elseBr)$ & 4        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
    $(29,30,\thenBr)$ & 1        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
    $(29,37,\elseBr)$ & 1        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
    $(38,39,\thenBr)$ & 2        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
    $(38,46,\elseBr)$ & 2        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
    $(47,48,\thenBr)$ & 3        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
    $(47,55,\elseBr)$ & 3        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
